ARIMA MODELS - without log-back transformations

### 2025-06-23 models_with_logback/ES_ADJACENT/ADJACENT.Rmd
update
comments review

---
title: "ADJACENT STATES ARIMAX MODEL - Influenza hospitalization data"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

This function utilizes ensembles and single automatic ARIMAX models which have mean cases by adjacent states as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. It return some metrics that evaluate the performance of the mod
els:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

>>>>

---
title: "ADJACENT STATES ARIMAX MODEL - with log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in states on the contiguous U.S. These model use mean hospitalizations in adjacent states as exogenous variables. The models fit on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

### 2025-06-23 models_with_logback/ES_ARIMA/ES_ARIMA.Rmd
comments review

---
title: "ARIMA ENSEMBLE MODELS - Influenza hospitalization data"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

This function utilizes ensembles and single automatic ARIMA models. The function fits a rolling window of 104 weeks to generate forecasts. It returns some metrics that evaluate the performance of the models: target_end_date, abs_error, cases, forecast, number of models, weighted interval score (WIS) and predictive quantiles (%). The user defines if it will use an AUTO ARIMA (auto=TRUE), or ensembles of 27 (ES27=TRUE) or ensembles of 64 models (ES64=TRUE). It can also choose the number of weeks ahead for each forecast, and the size of the rolling window which is set as 104 (2 years).

>>>>

---
title: "ARIMA MODELS - with log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

Here we run ensembles and single automatic ARIMA models for forecasting weekly hospitalizations in states on the contiguous U.S. The models fit on a rolling window of previous 104 weeks to generate forecasts. It returns some metrics that evaluate the performance of the models: target_end_date, abs_error, cases, forecast, number of models, weighted interval score (WIS) and predictive quantiles (%). The user defines if it will use an AUTO ARIMA (auto=TRUE), or ensembles of 27 (ES27=TRUE) or ensembles of 64 models (ES64=TRUE). It can also choose the number of weeks ahead for each forecast, and the size of the rolling window which is set as 104 (2 years).

### 2025-06-23 models_without_logback/ES_ADJACENT/ADJACENT.Rmd
update
comments review

---
title: "ADJACENT STATES ARIMAX MODEL - Influenza hospitalization data"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

This function utilizes ensembles and single automatic ARIMAX models which have mean cases by adjacent states as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. It return some metrics that evaluate the performance of the mod
els:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

>>>>

---
title: "ADJACENT STATES ARIMAX MODEL - without log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in states on the contiguous U.S. These model use mean hospitalizations in adjacent states as exogenous variables. The models fit on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models do not include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

### 2025-06-23 models_without_logback/ES_ARIMA/ES_ARIMA.Rmd
comments review

---
title: "ARIMA MODELS - with log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

>>>>

---
title: "ARIMA MODELS - without log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---
